TBD

### 2021-02-21 outputs/paper/paper.Rmd
Formatting changes
Superscripts added correctly.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)
library(purrr)
#devtools::install_github("johannesbjork/LaCroixColoR")
library(LaCroixColoR)

@@

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####

### Format percent
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}

### Format table for Chi-squared test
tableChisq <- function(capt, stat, df, p) {   
  chi_stat <- c(stat)
  chi_param <- c(df)
  chi_p <- c(p)
  chi_df <- data.frame(chi_stat, chi_param, paste(chi_p,"*"))

  kable(chi_df,
        digits = 2,
        caption = capt,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(symbol = "The Chi-squared statistic is significant at the 0.05 level") %>%
    kable_paper(c("striped", "hover"))
}

@@

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure 5 shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, Figure 6 shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2 (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2 (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery (Figure 7).

@@

Pearson’s Chi-squared test is used to see if there is a statistically significant difference between the intervention and the adjustments of the restaurants. The test results show that the p-value of each of those adjustments is close to 0 (*p* < 2.2e-16), meaning that there is a high correlation between those two variables. Consequently, it is expected that restaurants will adjust the menu price and reduce their operating schedule if they operate on a delivery and take-out only basis.

@@

### Chi-squared test
q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type) %>%
  chisq.test()

tableChisq("Pearson's Chi-squared Test for Q14", q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)

@@

```{r Q16, echo = FALSE, message = FALSE}
### Have you applied for and received any external funding or grants for your restaurant since (intervention start date)?
### Yes
### No

ggplot(data = all_simulated_dataset, mapping = aes(x = Q16, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Application status",
       y = "# of restaurants",
       title = str_wrap("Funding Applications between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)
#devtools::install_github("johannesbjork/LaCroixColoR")
library(LaCroixColoR)

@@

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}
```

@@

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure 5 shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, Figure 6 shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2^ (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2^ (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery (Figure 7).

@@

Pearson’s Chi-squared (*X*^2^) test is used to see if there is a statistically significant difference between the intervention and the adjustments of the restaurants. The test results show that the p-values of all adjustments are extremely close to 0, meaning that there is a high correlation between those variables. Consequently, it is expected that restaurants will adjust the menu price and reduce their operating schedule if they operate on a delivery and take-out only basis.

@@

q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type)
chisq.test(q14_chi)
```

@@
